---
title: "Visualization_1"
author: "Jiayi Shen"
date: "9/26/2018"
output: html_document
---

```{r setup, include=FALSE}

#setting up the output format of graphs
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(ggridges)
```

`cache = TRUE` 
```{r data_import, cache = TRUE}
install.packages("devtools")
library("devtools")
install_github("ropensci/rnoaa")

library(rnoaa)

weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```


## Basic Scatter Plot:
1. define the dataset we are using 
2. define aesthetic mapping
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

Alternatively, we can use ` %>% ` to avoid storing any intermediate varaibles, or data filtering steps.
```{r}
weather_df %>%
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()+
  geom_smooth(se = FALSE)
```

Smoothing methods:
lm() for linear smooths, glm() for generalised linear smooths, loess() for local smooths
`se=FALSE` turns of standard error bars. 
`alpha` defines the transparency of the plots.


###Facetting...

```{r}
ggplot(weather_df, aes(x = tmax, y = tmin, color = name)) + geom_smooth()
ggplot(weather_df, aes(x = tmax, y = tmin)) + geom_smooth(aes(color = name))
```

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```
 
can also remove the color=name command in the first line, but loses the colors. 


Try different styles:
```{r}
ggplot(weather_df, aes(x = tmax, y = tmin)) + geom_bin2d()
ggplot(weather_df, aes(x = tmax, y = tmin)) + geom_density2d()
```



## Other interesting plots
looking at tmax V.S. season/date
```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + geom_line()
```

Adding in precipitation by adding `size = prcp` to `geom_point`
```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```


##univariate plots

comparing two lines of code:
whether or not include the color="blue" in the aesthetic mapping argument. 
In the second line: ggplot is looking for a variable called blue
```{r}
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin), color = "blue")
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin, color = "blue"))
```

Histograms
```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram()
```
Without saying any specifications, `geom_histogram` produces an overlapped higtogram which is difficiult to read. So we can do the following:

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge", binwidth = 2)
```
The position = "dodge" places the bars for each group side-by-side

##Density plot

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")

```

Splitting the three categories into there subplots & filling the ridges of density curve.
```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```


## Make a bunch of plots

```{r}
ggplot(weather_df, aes(y = prcp, x = name)) + 
  geom_boxplot() 
```

```{r}
ggplot(weather_df, aes(y = prcp, x = name)) + 
  geom_violin() 
```

```{r}
ggplot(weather_df, aes(x = prcp, fill = name)) + 
  geom_density(alpha = .5)
```

```{r}
weather_df %>% 
  filter(prcp > 100) %>% 
  ggplot(aes(x=prcp, fill = id)) + geom_density(alpha = .5)
```

